Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
Simplify reference to `import_notes()`

Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].

>>>>

Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
A custom R function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].
